---
title: "SAS for P8120"
author: "Columbia University, Department of Biostatistics"
output: html_document
self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, out.width = "10%"}
htmltools::img(src = knitr::image_uri("../logos/p8120_logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:300px; padding:10px; width:125px; height:125px;')
```

<br>

This document is intended to be used as a guide to SAS for P8120 (Analysis of Categorical Data). This document is not exhaustive; please consult one of the TA's, Dr. Mauro, or the online SAS user guide for more help if needed. 

### Importing data

Importing data in SAS can be done a couple of different ways. We recommend using one of two methods: the import procedure or a data step. 

The import procedure is the most straightforward way of importing data into SAS. The procedure requires two arguments and a third optional requirement is recommended: `out`, `datafile`, and `dbms`. The `out` argument specifies the name of the newly created SAS dataset; the `datafile` argument specifies the complete path for the file containing the data to be imported in quotation marks; the `dbms` argument is optional and specifies the file type to be parsed. The most commonly used identifiers are `csv`, `tab`, `xlsx`, and `dlm`. If importing a csv file, this argument is not necessary. The syntax is as follows: 

```{}
proc import out = <SAS dataset name>
            datafile = "filepath"
            dbms = <identifier> replace;
```

The data step in SAS is where all data manipulation occurs, this includes being able to import data. 


### Hypothesis tests

Use the following table to locate procedures for hypothesis tests. If you are unsure of the usage of a procedure, refer to the online SAS guide.

|Hypothesis test                     | SAS procedure                  |
|------------------------------------|--------------------------------|
|One/two sample test proportions, normal approximation  || 
|One/two sample test proportions, exact   |            | 
|Confidence intervals, proportions   | | 
|Chi-squared                         ||
|Fisher's exact                      ||
|McNemar's test                      ||
|Logistic regression                 | `proc logistic` | 
|GOF & Hosmer Lemeshow               | |
|Conditional logistic regression     | | 
|Cochran Armitage Trend test         | | 
|Brewlow Day test                    | | 

### Measures of association

| Measure               | SAS procedure      |
|-----------------------|--------------------|
|Odds ratio (2xk table) |     |
|Risk ratio (2xk table) |     |
|Risk difference        |     |
### Power

