---
title: "SAS for P8120"
author: "Columbia University, Department of Biostatistics"
output: html_document
self_contained: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, echo=FALSE, out.width = "10%"}
htmltools::img(src = knitr::image_uri("../logos/p8120_logo.png"), 
               alt = 'logo', 
               style = 'position:absolute; top:0; right:300px; padding:10px; width:125px; height:125px;')
```

<br>

### Importing data

Importing data in SAS can be done a couple of different ways. We recommend using one of two methods: using the import procedure or a data step. 

### Hypothesis tests

Use the following table to locate procedures for hypothesis tests. If you are unsure of the usage of a procedure, refer to the online SAS guide.

|Hypothesis test                     | SAS procedure                  |
|------------------------------------|--------------------------------|
|One/two sample test proportions, normal approximation  |`prop.test()`| 
|One/two sample test proportions, exact   | `binom.test()`            | 
|Confidence intervals, proportions   | `BinomCI()`                    | 
|Chi-squared                         | `crosstab(..., chisq = TRUE)` |
|Fisher's exact                      | `crosstab(..., fisher = TRUE)`|
|McNemar's test                      | `crosstab(..., mcnemar = TRUE)`|
|Logistic regression                 | `glm(..., family = binomial)`  | 
|GOF & Hosmer Lemeshow               | TBD                            |
|Conditional logistic regression     | `clogit()`                     | 
|Cochran Armitage Trend test         | `CocrhanArmitageTest()`        | 
|Brewlow Day test                    | `BreslowDayTest`               | 

### Measures of association

| Measure               | R function         | Package
|-----------------------|--------------------|----------
|Odds ratio (2xk table) | `oddsratio()`      | epitools
|Risk ratio (2xk table) | `riskratio()`      | epitools
|Risk difference        | `riskdiff()`       | catfun

### Power

